% Created 2017-03-11 Sat 14:55
\documentclass[t,presentation]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\newcommand{\T}{\top}
\newcommand{\E}{\ensuremath{\mbox{E}}}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\R}{\ensuremath{\mathbb{R}}}
\newcommand{\Eq}[1]{(\ref{eq:#1})}
\newtheorem{proposition}{Proposition} \newcommand{\Prop}[1]{Proposition \ref{prop:#1}}
\newcommand{\Fig}[1]{Figure \ref{fig:#1}} \newcommand{\Tab}[1]{Table \ref{tab:#1}}
\usetheme{Madrid}
\usecolortheme{}
\usefonttheme{}
\useinnertheme{}
\useoutertheme{}
\date{March 11, 2017}
\title{Two Capital Transfers in South Sudan (2013-2015)}

\hypersetup{
 pdfauthor={Elliott Collins},
 pdftitle={Two Capital Transfers in South Sudan (2013-2015)},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 24.5.1 (Org mode 8.3.2)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section*{A Multifaceted Asset Transfer Program}
\label{sec:orgheadline3}

\begin{frame}[label={sec:orgheadline1}]{Targetting the Ultra-Poor (TUP)}
\begin{itemize}
\item ``Very poor'' households face physical and human capital constraints
\item BRAC started a program to address both:

\begin{itemize}
\item Microenterprise training (\(\approx\) 1 week)
\item \alert{Capital transfers} (Relatively large, enterprise-specific)
\item Monitoring \& support
\item Savings Encouragement
\end{itemize}

\item Goal is to provide a new, sustained source of income
\end{itemize}
\end{frame}

\begin{frame}[label={sec:orgheadline2}]{Evidence:}
\begin{itemize}
\item \alert{Bandiera et al.} Evaluates original TUP program in Bangladesh
\begin{itemize}
\item Increase in self-employment 15pp
\item 7\% increase in expenditure
\item Increased productive asset holdings
\end{itemize}
\item \alert{Banerjee et al.} evaluate 6 more experiments\footnote{Ethiopia, Ghana, Peru, Honduras, India, Pakistan}
\begin{itemize}
\item Similar in magnitude to Bandiera et al.
\item .122 sd increase in consumption, .25 sd increase in asset holdings
\end{itemize}
\end{itemize}
\end{frame}

\section*{Cash Transfers}
\label{sec:orgheadline6}
\begin{frame}[label={sec:orgheadline4}]{Cash Transfers}
Lots of experiments on cash transfers

\begin{itemize}
\item \alert{Haushofer \& Shapiro (2013):} UCT's in Kenya

\begin{itemize}
\item 20\% increase in food consumption
\item 58\% increase in assets
\end{itemize}
\item \alert{Blattman \emph{et al.} (2015)} give \$150 USD to women in Uganda (and form ``support groups'')

\begin{itemize}
\item 15\% \(\uparrow\) in consumption
\item \(\approx\) 40\% \(\uparrow\) in productive assets held
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[label={sec:orgheadline5}]{An alternative to TUP-type programs}
Relative to Cash Transfers:

\begin{itemize}
\item TUP programs have high fixed \alert{and} marginal costs
\item \emph{And} constrain investment of new capital to a given activity
\item Offers several additional forms of support
\item \alert{Different welfare implications?}
\end{itemize}

We compare cash and TUP programs in southern South Sudan (Yei county).

\begin{itemize}
\item High poverty rate, inflation, and political uncertainty
\end{itemize}
\end{frame}

\section*{BRAC's Experiment in South Sudan}
\label{sec:orgheadline9}

\begin{frame}[label={sec:orgheadline7}]{The TUP Program}
\begin{itemize}
\item Two short trainings (\(\approx\) 5 days)

\begin{itemize}
\item General business skills (numeracy, bookkeeping)
\item Enterprise-specific skills
\end{itemize}

\item Assets: Farming, ducks, goats, or small trade

\begin{itemize}
\item Total market value \$350 or \$410
\item Accounts for 80-90\% of average mariginal cost of enrollment
\end{itemize}

\item Weekly group meetings (modeled on MFIs) for 12 months
\end{itemize}
\end{frame}

\begin{frame}[label={sec:orgheadline8}]{Cash Transfers}
\begin{itemize}
\item Market value of TUP transfers measured at \$350-410

\item 125 eligible HH's received the same amount in cash

\item Gives the TUP framework an economically interesting, policy-relevant counterfactual

\item Not announced to HH's until week before (no ex-ante change in expectations)
\end{itemize}
\end{frame}

\section*{Complications}
\label{sec:orgheadline12}

\begin{frame}[label={sec:orgheadline10}]{Timing of Transfers}
\begin{itemize}
\item Asset transfers in December 2013 and March 2014

\begin{itemize}
\item Interrupted by conflict
\item Had not yet seriously spread to Yei
\item (No record of transfer dates)
\end{itemize}

\item Cash transfers completed June-July 2014

\item Midline survey in 2014, immediately before cash transfers.

\item Endline in 2015

\begin{itemize}
\item 12-13 months after UCT's
\item 14 or 18 months after asset transfers
\item An eventful 6 months\ldots{}
\end{itemize}

\item Monthly Mobile Survey in 2016

\begin{itemize}
\item Collected 6 consumption items for 6 months
\item Yields longer-term consumption estimates
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[label={sec:orgheadline11}]{Empirical Specification}
\begin{equation*}
Y_{it} =\sum_{t=2014}^{2015}\delta_{t}+\beta_{t}^{Cash}I_{t}*Cash_{it}+\beta_{t}^{TUP}I_{t}*TUP_{it}+\gamma Y_{i,2013}+\epsilon_{i}
\end{equation*}

\begin{itemize}
\item \(\delta_{t}\): Time FE's,  \(I_{2014}= 1 if t==2014\)
\item Estimate four treatment effects, \((2014,2015)\times(TUP,Cash)\)
\item \(\beta^{CSH}_{2014}\) is a placebo test.
\item Test \(\beta^{CSH}_{2015} = \beta^{TUP}_{2014}\) and \(\beta^{CSH}_{2015} = \beta^{TUP}_{2015}\)
\end{itemize}
\end{frame}

\section*{Results}
\label{sec:orgheadline22}

\begin{frame}[label={sec:orgheadline13}]{Results: Asset Holdings}
\begin{itemize}
\item Large effects on asset stock for TUP but not UCT's
\end{itemize}

\begin{center}
\begin{tabular}{lll}
\hline
 & Total & Productive\\
\hline
CTL mean & \(1225.61\) & \(337.60\)\\
\hline
TUP*2014 & \(535.79^{***}\) & \(361.80^{***}\)\\
 & \((154.02)\) & \((74.19)\)\\
TUP*2015 & \(624.79^{***}\) & \(320.74^{***}\)\\
 & \((146.01)\) & \((68.68)\)\\
CSH*2014 & \(-125.86\) & \(18.50\)\\
 & \((191.31)\) & \((95.80)\)\\
CSH*2015 & \(-49.99\) & \(5.00\)\\
 & \((187.32)\) & \((88.40)\)\\
\hline
N & \(1305.00\) & \(1247.00\)\\
\hline
\(\beta^{TUP}_{2015}-\beta^{CSH}\) & \(674.78^{***}\) & \(325.74^{***}\)\\
 & \((194.72)\) & \((92.26)\)\\
\hline
\end{tabular}
\end{center}
\end{frame}

\begin{frame}[label={sec:orgheadline14}]{Results: Consumption}
\begin{center}
\begin{tabular}{lllll}
\hline
 & Tot & Food & Non-durable & Durable\\
\hline
CTL mean & \(39.80^{*}\) & \(27.46^{*}\) & \(9.73\) & \(3.07\)\\
\hline
TUP*2014 & \(9.34^{***}\) & \(6.12^{***}\) & \(1.94^{*}\) & \(1.28^{**}\)\\
 & \(( 2.26)\) & \(( 1.57)\) & \(( 1.02)\) & \(( 0.50)\)\\
TUP*2015 & \(1.69\) & \(0.72\) & \(1.13\) & \(0.09\)\\
 & \(( 2.15)\) & \(( 1.50)\) & \(( 0.96)\) & \(( 0.47)\)\\
CSH*2014 & \(-1.03\) & \(-0.97\) & \(0.96\) & \(-0.38\)\\
 & \(( 2.80)\) & \(( 1.95)\) & \(( 1.28)\) & \(( 0.62)\)\\
CSH*2015 & \(5.66^{**}\) & \(3.50^{*}\) & \(2.17^{*}\) & \(0.06\)\\
 & \(( 2.75)\) & \(( 1.91)\) & \(( 1.24)\) & \(( 0.61)\)\\
TUP*2016 & \(-1.22^{*}\) & \(-1.18^{**}\) &  & \\
 & \(( 0.69)\) & \(( 0.53)\) &  & \\
CSH*2016 & \(1.74^{**}\) & \(0.74\) &  & \\
 & \(( 0.86)\) & \(( 0.66)\) &  & \\
\hline
N & \(1305.00\) & \(1295.00\) & \(1296.00\) & \(1260.00\)\\
\hline
\(\beta^{TUP}_{2015}-\beta^{CSH}\) & \(-3.97\) & \(-2.78\) & \(-1.04\) & \(0.03\)\\
 & \(( 2.85)\) & \(( 1.98)\) & \(( 1.30)\) & \(( 0.64)\)\\
\hline
\end{tabular}
\end{center}
\end{frame}

\begin{frame}[label={sec:orgheadline15}]{Savings (Total)}
\begin{itemize}
\item TUP group has more food saved, then more cash.
\item Useful to look at extensive margin\ldots{}
\end{itemize}

\begin{center}
\begin{tabular}{lll}
\hline
 & Savings & Food Sav\\
\hline
CTL mean & \(78.70\) & \(65.85\)\\
\hline
CSH*2014 & \(32.37\) & \(5.00\)\\
 & \((45.88)\) & \((10.38)\)\\
CSH*2015 & \(32.22\) & \(-9.60\)\\
 & \((45.88)\) & \((10.38)\)\\
TUP*2014 & \(18.53\) & \(26.08^{***}\)\\
 & \((36.31)\) & \(( 8.22)\)\\
TUP*2015 & \(101.17^{***}\) & \(-5.03\)\\
 & \((36.31)\) & \(( 8.22)\)\\
\hline
\(\beta^{TUP}_{2014}-\beta^{CSH}\) & \(-13.68\) & \(35.68\)\\
\(\beta^{TUP}_{2015}-\beta^{CSH}\) & \(68.96\) & \(4.57\)\\
N & \(2250.00\) & \(2250.00\)\\
\hline
\end{tabular}
\end{center}
\end{frame}

\begin{frame}[label={sec:orgheadline16}]{Savings (Extensive)}
\begin{itemize}
\item \(\approx\) 18\% - 30\% of TUP households report having some cash savings
\end{itemize}

\begin{center}
\begin{tabular}{lll}
\hline
 & Savings > 0 & Food Sav > 0\\
\hline
CTL mean & \(0.39\) & \(0.54\)\\
\hline
CSH*2014 & \(0.03\) & \(0.08\)\\
 & \(( 0.05)\) & \(( 0.06)\)\\
CSH*2015 & \(0.01\) & \(0.02\)\\
 & \(( 0.05)\) & \(( 0.05)\)\\
TUP*2014 & \(0.29^{***}\) & \(0.13^{***}\)\\
 & \(( 0.04)\) & \(( 0.04)\)\\
TUP*2015 & \(0.18^{***}\) & \(-0.03\)\\
 & \(( 0.04)\) & \(( 0.04)\)\\
\hline
\(\beta^{TUP}_{2014}-\beta^{CSH}\) & \(0.28^{***}\) & \(0.10\)\\
 & \(( 0.06)\) & \(( 0.07)\)\\
\(\beta^{TUP}_{2015}-\beta^{CSH}\) & \(0.18^{***}\) & \(-0.05\)\\
 & \(( 0.05)\) & \(( 0.05)\)\\
N & \(1500.00\) & \(1500.00\)\\
\hline
\end{tabular}
\end{center}
\end{frame}

\begin{frame}[label={sec:orgheadline17}]{Savings (Intensive)}
HH's with any savings: \(\beta_{\text{UCT}}\) \(\approx\) 90 SSP (47\%), \(\beta_{\text{TUP}}\) \(\approx\) 81 (42\%)
\begin{center}
\begin{tabular}{lll}
\hline
 & Savings & Food Sav\\
\hline
CTL mean & \(191.19\) & \(114.78\)\\
\hline
CSH*2014 & \(28.74\) & \(0.22\)\\
 & \((42.93)\) & \((15.38)\)\\
CSH*2015 & \(91.40^{**}\) & \(-14.34\)\\
 & \((40.89)\) & \((14.98)\)\\
TUP*2014 & \(-27.09\) & \(17.16\)\\
 & \((29.76)\) & \((12.33)\)\\
TUP*2015 & \(81.33^{***}\) & \(1.13\)\\
 & \((29.32)\) & \((12.26)\)\\
\hline
\(\beta^{TUP}_{2014}-\beta^{CSH}\) & \(-118.49^{**}\) & \(31.50\)\\
 & \((50.48)\) & \((19.40)\)\\
\(\beta^{TUP}_{2015}-\beta^{CSH}\) & \(-10.07\) & \(15.47\)\\
 & \((40.86)\) & \((16.10)\)\\
N & \(671.00\) & \(777.00\)\\
\hline
\end{tabular}
\end{center}
\end{frame}

\begin{frame}[label={sec:orgheadline18}]{Land Use (Total)}
Cash Transfers result in significantly less agricultural land use

\begin{center}
\begin{tabular}{lll}
\hline
Area (Fedan) & Cult Land & Own Land\\
\hline
CTL mean & \(59.90\) & \(53.51\)\\
\hline
CSH*2014 & \(15.83\) & \(16.75\)\\
 & \((19.90)\) & \((16.07)\)\\
CSH*2015 & \(-45.09^{**}\) & \(-43.52^{***}\)\\
 & \((17.86)\) & \((16.07)\)\\
TUP*2014 & \(-7.08\) & \(1.13\)\\
 & \((15.90)\) & \((12.83)\)\\
TUP*2015 & \(-15.55\) & \(-17.66\)\\
 & \((14.28)\) & \((12.83)\)\\
\hline
\(\beta^{TUP}_{2015}-\beta^{CSH}\) & \(29.54\) & \(25.86\)\\
\hline
N & \(1893.00\) & \(2063.00\)\\
\hline
\end{tabular}
\end{center}
\end{frame}

\begin{frame}[label={sec:orgheadline19}]{Income}
\begin{itemize}
\item TUP group substituted away from farmwork to livestock
\item Both have \emph{less} income from farming and agricultural wage labor
\end{itemize}

\begin{longtable}{lrrrrrrr}
\label{tab:orgtable1}

\\
\hline
 & Total & Farm & Livestock & Non-Farm\\
\hline
\endfirsthead
\multicolumn{5}{l}{Continued from previous page} \\
\hline

 & Total & Farm & Livestock & Non-Farm \\

\hline
\endhead
\hline\multicolumn{5}{r}{Continued on next page} \\
\endfoot
\endlastfoot
\hline
CTL mean & \(4325.54\) & \(773.05\) & \(640.33\) & \(3774.49\)\\
\hline
TUP & \(327.83\) & \(-142.20^{*}\) & \(281.12^{**}\) & \(86.24\)\\
 & \((455.95)\) & \((77.21)\) & \((126.30)\) & \((469.48)\)\\
CSH & \(7.92\) & \(-26.15\) & \(-83.81\) & \(61.80\)\\
 & \((600.43)\) & \((100.82)\) & \((177.25)\) & \((620.53)\)\\
\hline
\(\beta^{TUP}-\beta^{CSH}\) & \(319.91\) & \(-116.05\) & \(364.94^{**}\) & \(24.44\)\\
 & \((629.93)\) & \((105.79)\) & \((174.74)\) & \((651.27)\)\\
\hline
N & \(671.00\) & \(531.00\) & \(380.00\) & \(606.00\)\\
\hline
\end{longtable}
\end{frame}

\begin{frame}[label={sec:orgheadline20}]{What did the cash get used for?}
Simply asking what cash transfer households bought:

\begin{center}
\begin{tabular}{lrrr}
\hline
Use & \% >0 & Avg. Amt & Std\\
\hline
School & 0.52 & 266 & 214\\
Sick & 0.472 & 234 & 203\\
Food & 0.472 & 150 & 202\\
Inventory & 0.464 & 390 & 716\\
Save & 0.36 & 193 & 190\\
Livestock & 0.344 & 249 & 186\\
clothes & 0.32 & 136 & 160\\
Renovations & 0.264 & 110 & 123\\
\hline
\end{tabular}
\end{center}
\end{frame}

\begin{frame}[label={sec:orgheadline21}]{Conflict}
TUP group less likely to report being affected or having forgone investment by conflict.

(The violence was mostly distant at the time.)

\begin{center}
\begin{tabular}{llllll}
\hline
 & Affected & Not Invest & Migrated & No Means & ProtectLives\\
\hline
CTL mean & \(0.53^{***}\) & \(0.16^{***}\) & \(0.33^{***}\) & \(0.33^{***}\) & \(0.38^{***}\)\\
\hline
TUP & \(-0.13^{***}\) & \(-0.06^{**}\) & \(0.04\) & \(-0.06\) & \(0.02\)\\
 & \(( 0.04)\) & \(( 0.03)\) & \(( 0.04)\) & \(( 0.04)\) & \(( 0.05)\)\\
\hline
N & \(601.00\) & \(655.00\) & \(655.00\) & \(655.00\) & \(585.00\)\\
F-stat & \(9.20\) & \(3.95\) & \(0.96\) & \(2.55\) & \(0.19\)\\
\hline
\end{tabular}
\end{center}
\end{frame}

\section*{Interpretation and Speculation}
\label{sec:orgheadline26}

\begin{frame}[label={sec:orgheadline23}]{Summary}
\begin{itemize}
\item TUP group reports significantly higher assets stock and savings in 2015.

\item Cash group reports higher savings (intensive) and consumption 
\begin{itemize}
\item No asset effects, in contrast with previous experiments
\end{itemize}

\item Cash group moved away from farming. TUP group moved specifically towards livestock.

\item TUP group less likely to report being affected by the conflict (in 2015.)

\item \(\beta^{TUP}_{2015}=\beta^{Cash}_{2015}\) rejected for asset wealth and Pr(savings>0).
\end{itemize}
\end{frame}

\begin{frame}[label={sec:orgheadline24}]{Interpretation}
Possible interpretations:

\begin{itemize}
\item Cash results consistent with climate of uncertainty and high inflation.

\begin{itemize}
\item Little investment or illiquid savings. Less land ownership. Focus on \emph{spending} money.
\end{itemize}

\item Both treatments increased short-term consumption. Neither significantly increased total income.

\item TUP framework has some success at increasing wealth \& security in a context where cash transfers may have atypically few long-term effects.
\end{itemize}
\end{frame}

\begin{frame}[label={sec:orgheadline25}]{Thank you}
\begin{center}
\begin{tabular}{l}
\hline
\\
\hline
\\
Thank You!\\
\\
\hline
\\
\hline
\end{tabular}
\end{center}
\end{frame}
Emacs 24.5.1 (Org mode 8.3.2)
\end{document}
